\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3.4cm,lmargin=3cm,rmargin=3.4cm}
\usepackage{setspace}
\onehalfspacing
\usepackage{babel}
\begin{document}
\begin{center}
\textbf{\textit{\LARGE{Revision of }}}\textbf{\LARGE{MissingDataGUI\bigskip{}
}}
\par\end{center}{\LARGE \par}

The substantial changes were made on both the package and the manuscript.
The main changes of the package include:

\begin{itemize}
\item embedding two more packages (mice and mi) for multiple imputation;
\item adding a new imputation method based on the nearest neighbors;
\item enabling multiple tabs in the graphics widget, to compare different
imputation methods and multiple imputation chains;
\item adding a setting tab in the GUI to adjust the parameters and the imputation
methods of mice;
\item allowing the input variables to be the ordered factors.
\end{itemize}
The main changes in the article include:
\begin{itemize}
\item introduction and comparison among the current multiple imputation
packages in R;
\item example of how to check the missing assumptions;
\item more background of the plot types;
\item explicit explanation on the imputation methods of the nearest neighbors;
\item comparison among the multiple imputation chains.
\end{itemize}

\section*{Answers to Review 1}
\begin{enumerate}

\item What action should the user take in response to the generated plots?
(Para. 1 \& 6)
\begin{itemize}
\item In our revision, the examples are explained more explicitly with some
conclusion and suggestion. For instance, in the example of missingness
map, we suggest users to use parallel coordinates plot to reveal the
dependent variables on the missing of two highly associated variables
before the imputation. Also, we introduce how to use the GUI to check
the missing assumptions.
\end{itemize}

\item There are problems in reproducing Figure 5. (Para. 2)
\begin{itemize}
\item We do not have any problem in reproducing Figure 5. MissingDataGUI
has released a new version, so hopefully the problem could be fixed.
\end{itemize}

\item Ordinal variables are omitted. (Para. 4)
\begin{itemize}
\item Ordinal variables are accepted now. Median could be obtained as the
center after sorted. Methods provided by the package mice can be used
for the ordinal variables too.
\end{itemize}

\item It is not clear what happens when the user conditions on a factor
that itself has missingness. (Para. 5)
\begin{itemize}
\item It is treated as a separate group if the conditioning variable is
not selected to be imputed.
\end{itemize}

\item Missingness map: what should the user do with the positive or negative
association? (Para. 7)
\begin{itemize}
\item We use a new example to illustrate the missingness map, which shows
a positive association. The reason of the association in the example
is explained and the corresponding suggestion is provided. However,
one example cannot cover all the situations, so the reason and suggestion
are not general. Users should consider the actual circumstance before
any action.
\end{itemize}

\item In section 3.2, the authors choose an imputation algorithm to maximize
the similarity, however, it is neither necessary nor sufficient to
indicate whether the imputations are reasonable (Para. 8)
\begin{itemize}
\item The review is correct that it is neither necessary nor sufficient
to use the similarity to indicate whether the imputations are reasonable.
\end{itemize}

\item The package supports so many imputation algorithms that are known
to have poor theoretical properties. Why are the others supported,
which invariably means that some users will utilize them? (Para. 9)
\begin{itemize}
\item The simple imputation methods like overall mean and median, are practical,
though not ideal.
\item A couple of imputation methods were added to the package, including
two multiple imputation packages: mice and mi.
\end{itemize}

\item The parallel coordinates plot could be used to visualize whether the
completed data set is consistent with the missing-at-random (MAR)
assumption. (Para. 10)
\begin{itemize}
\item An example was added to Section 3 on how to use the parallel coordinates
plot and other plots to check the missing assumptions. MCAR (missing
completely at random) can be checked, but MAR is not testable. However,
it is possible to suggest the dependent variables via the plots.
\end{itemize}

\end{enumerate}

\section*{Answers to Review 2}
\begin{enumerate}

\item It does not even clearly warn against using univariate imputation
approaches for multivariate analysis purposes. (Para. 2)
\begin{itemize}
\item This issue cannot be answered easily by adding a warning under that
situation. This package is designed for the novice users to explore
and understand the missing structure by trying various imputation
methods. We know that the univariate imputation methods do not help
much to get an accurate estimate, so we provide other multivariate
methods. We never recommend the univariate ones over others. Since
the users could load any types of data into the GUI, we have no idea
if the multivariate analysis is appropriate, or if the variables are
independent in a multivariate analysis. For any real data, users usually
start from an exploration, before knowing which impuation method to
use. The univariate methods are handy and practical at the beginning
of an analysis. A warning saying that the univariate imputation is
risky may not be correct all the time, and we do not want to prevent
the users from trying different methods than what they ``should''
use.
\end{itemize}

\item How the variables used in regression imputation are chosen? (Para.
2)
\begin{itemize}
\item The variables can be selected in area 1 of Figure 1. All of the selected
variables are thrown into the model. The regression method is a multiple
imputation method provided by the package Hmisc, and renamed to ``MI:
areg'' in the new version.
\end{itemize}

\item How several imputations from multiple imputation are used in plotting?
(Para. 2)
\begin{itemize}
\item In the revision we allow the users to pick the number of imputation
sets in any multiple imputation. Different sets are plotted in different
tabs.
\end{itemize}

\item For the less well-known types of plot, e.g. the spine plot, a brief
description should be given. (Para. 2)
\begin{itemize}
\item Descriptions and references are given for most of the plot types in
the revision.
\end{itemize}

\item Some other related packages are completely ignored (Para. 3)
\begin{itemize}
\item Now they are briefly introduced in Section 1, and the comparison of
the multiple imputation packages is given in Section 2.3.
\end{itemize}

\item Installation issues (Para. 4, Bullet 1)
\begin{itemize}
\item The installation of Gtk+ on Windows is not fun since Windows users
may need to edit the environment variable PATH manually. Once you
get this step done, it should be easy to install RGtk2 and gWidgetsRGtk2
in R.
\end{itemize}

\item Pairwise plot does not work on Windows R 3.0.1. (Para. 4, Bullet 2)
\begin{itemize}
\item In a recent test we don't see this problem. Could you please update
to the latest versions of R and the packages, and try again? If it
still doesn't work, please send me the error message and the system
information.
\end{itemize}

\item Warning message ``ggpcp is deprecated''. (Para. 4, Bullet 3)
\begin{itemize}
\item Fixed in version 0.2-0 of the package.
\end{itemize}

\item When creating a numerical summary of missingness for the complete
dataset, why do I have to select all variables? (Para. 5, Bullet 1)
\begin{itemize}
\item Now if no variables are selected, then the numerical summary will
include all the variables. Shift + left-click will make it easy to
select all.
\end{itemize}

\item Why doesn\textquoteright{}t conditioning affect the numerical summary?
(Para. 5, Bullet 2)
\begin{itemize}
\item Fixed in version 0.2-0.
\end{itemize}

\item In the parallel coordinate plot, switch plotting order so that the
missings are displayed on top of the non-missings. (Para. 5, Bullet
3)
\begin{itemize}
\item Fixed in version 0.2-0.
\end{itemize}

\item As many people are red-green blind, choosable colors or at least a
better choice of predefined colours would be helpful. (Para. 5, Bullet
4)
\begin{itemize}
\item We change the color scheme to make it colorblind friendly.\end{itemize}
\end{enumerate}

\end{document}
